Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-23 article.Rmd
Fix typos in .tex and .md versions

---
title: "Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Joey Talbot, Malcolm Morgan, Martin-Lucas-Smith"
output: bookdown::github_document2
# output: bookdown::html_document2
# output:
#   bookdown::pdf_document2:
#     keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---

>>>>

---
title: "Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Joey Talbot, Malcolm Morgan, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
output:
  bookdown::pdf_document2:
    keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---

### 2020-06-23 article.tex
Update paper
Fix typos in .tex and .md versions

In the context of reduced public transport capacity in the wake of the COVID-19 pandemic, governments are scrambling to enable walking and cycling while adhering to physical distancing guidelines.
A range of pop-up options exist, include road space reallocation, which represents a `quick win' for cities with `spare space' along continuous road sections that have high latent cycling potential.
We developed methods to condense the complexity of city networks down to the most promising roads for road space reallocation schemes.
The resulting Rapid Cycleway Prioritisation Tool has been deployed for all local and regional transport authorities in England to help prioritise emergency funds for new cycleways nationwide.
The methods and concepts could be used to support investment in pop-up infrastructure in cities worldwide.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/widenmypath} \includegraphics[width=1\linewidth]{figures/saferstreets} \caption{Screenshots from the websites widenmypath.com (top) which includes top cycle route recommendations generated using the methods outlined in this paper in an open web forum, and salfordliveablestreets.commonplace.is (bottom) to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure.}\label{fig:commonplace}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/results-top-leeds} \caption{Results, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled.}\label{fig:res}
\end{figure}

@@

A major advantage of the approach is that it is scalable.
It would be feasible to internationalise the approach, given sufficient computer and developer resource to overcome the key data barriers: lack to cycling potential data and lack of road width data that are specific to the UK.
In summary, the methods presented can help lock-in the benefits of COVID-19 related cycling booms long term.

>>>>

In the context of reduced public transport capacity in the wake of the COVID-19 pandemic, governments are scrambling to enable walking and cycling while adhering to physical distancing guidelines.
A range of pop-up options exist, include road space reallocation, which represents a `quick win' for cities with `spare space' along continuous road sections that have high latent cycling potential.
We developed methods to condense the complexity of city networks down to the most promising roads for road space reallocation schemes.
The resulting Rapid Cycleway Prioritisation Tool has been deployed for all local and regional transport authorities in England to help prioritise emergency funds for new cycleways nationwide.
The approach could be used to support investment in pop-up infrastructure in cities worldwide.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/jpg/widenmypath} \includegraphics[width=1\linewidth]{figures/jpg/saferstreets} \caption{Screenshots from the websites widenmypath.com (top) which includes top cycle route recommendations generated using the methods outlined in this paper in an open web forum, and salfordliveablestreets.commonplace.is (bottom) to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure.}\label{fig:commonplace}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/results-top-leeds} \caption{Results of the Rapid Cycleway Prioritisation Tool, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled.}\label{fig:res}
\end{figure}

@@

A major advantage of the approach is that it is scalable.
It would be feasible to internationalise the approach, given sufficient computer and developer resource to overcome the key data barriers: lack of cycling potential and road width data.
In summary, the methods presented can help lock-in the benefits of COVID-19 related cycling booms long term.
